Keyphrase Extraction from User Generated Contents on Medical Domain

### 2017-05-25 paper.tex
Benerin Konsil
mangat

\section{Introduction}
Health-related or question-answering forum is becoming a trend today. With those forum, seeking health information and asking questions to doctors is pretty much easier. As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks in IR and NLP \cite{cao2010automatically}. However, understanding those various health-related contents, especially from an online forum, is simply not a trivial task since they are written in free text format (i.e. unstructured format), and often prone to grammatical and typographical glitches. Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.

@@

In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions from online forums, such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}. We present a new keyphrase extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated questions. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely in line with our goal since important keyphrases of a medical question can be used to formulate a query for the passage or question retrieval subsystem \cite{gong2009improving}. The following example shows the results of keyphrase extraction in a medical document:
	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}. Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}. apakah ada hubungannya dengan \textbf{diet mayo}? terima kasih sblumnya dok.}
	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}. And when the symptom occur it's \textbf{very hurt when breathing}. is there any connection with \textbf{moyo diet}? thanks before)}

@@

For medical document, Sarkar and Kamal \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles. They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.

Unfortunately, there are limited works regarding the task of keyphrase extraction from user generated on medical question, especially in Indonesian language. Similar research in English language has been conducted by Cao et al. \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health forum. They use information, such as word location and length as features in their experiments.

@@

\textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary. The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from Konsil Kedokteran Indonesia\footnote{www.
kki.go.id/assets/data/arsip/SKDI_Perkonsil,_11_maret_13.pdf.}. The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug. Based on this feature, we classified words by their appearance in the medical dictionary. We represent this feature as one-hot-vector.

@@

\textbf{Abbreviation and Acronym (Wa).} We also identified words by their appearance in abbreviation or acronym dictionary gathered by Abid \cite{skripsiKakAbid}. We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell's palsy". One-hot-vector is used to classify whether a word is an abbreviation/acronym or not. For example, the word "\textit{mengapa (why)}" sometimes is abbreviated to \texttt{mngp} by some patients.

@@

\textbf{Word Stickiness (Ws).} As a keyphrase, a sequence must be in a valid order. There is some noise such as misuse punctuation by users. For example, "\textit{Saya mengalami pusing pada jidat sakit perut dan pandangan kabur} (I am having a headache on forehead stomachache and blurred vision)", there is no comma between "jidat (forehead)", "sakit perut (stomachache)" and "dan (and)". Our model may mistake the sequence "(jidat sakit perut)forehead stomachache" as a keyphrase. Based on that problem, we propose a feature that may capture how likely of a given word is occurred together with the word before and after. We use Pointwise Mutual Information (PMI) of a bigram probability to capture the likeness. Formula \ref{eq:pmi} is the formula for calculating the PMI value. In that formula, $p(x)$ is the occurrence probability of word $x$, $p(y)$ is the occurrence probability of word $y$, and $p(x, y)$ is the probability of word $x$ and $y$ co-occur together.
\begin{equation}\label{eq:pmi}
PMI(x,y)=log(\frac{P(x, y)}{P(x).P(y)})
\end{equation}
The feature function is formally described as $f_s(w) = [x, y]$ where $w$ is a word, x is the stickiness value between w and the word before, and y is the stickiness value between w and the word before. For example, the word "\texttt{cancer}" in sentence "\texttt{How to prevent cancer doc?}", the feature value is $f_s(cancer) = [0.56, 0.1]$ where $f_s$ is feature stickiness feature function. It is worth to note that the word "\texttt{cancer}" is rarely co-occur with the word "\texttt{doc}". Therefore, the stickiness value between the word "cancer" and "doc" is relatively smaller than "prevent".

We process the sequences word by word. All Features are extracted and concatenated into one vector from every word as the input representation of the model. The output of our model are labels which describe whether a word is either part of keyphrase or not.

@@

To get a better inference, information from the past and future of sequences can be integrated. This approach is proven effective in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}. Therefore, we utilized bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward. We concatenate the output from both LSTM. We build up to two layers of B-LSTM.

@@

We also experimented on customizing the way we input the features underneath our aforementioned model. Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to give some kind of weighting for every feature we have. 
\begin{equation}\label{eq:concat}
Z =  concatenate(F_{1}, F_{2}, ..F_{9})
\end{equation}
We argue that each feature has different contribution to the model. In order to do so, we create a new layer underneath our model to do the weighting scenario. Formally, let $Z$ is the input representation and $F_{i}$ are the extracted feature in vector form, $W_i \in {\rm I\!R^{a_i \times b}}$ where the length of $a$ is equal to $F_{i}$ and $b$ is the input representation vector. The following equation to weight all features can be seen in below:
\begin{equation}
Z =  tanh(W _{1}.F_{1} + W_{2}.F_{2} + .. + W_{n}.F_{9})
\end{equation}

\section{Evaluations and Results}
\subsection{Data Collection}
To develop training data, we collected question-answer pairs which previously crawled from Indonesian question-answering medical forum. Then, we removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs. Finally, we manually annotated 416 questions. The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}.

@@

		\bottomrule
	\end{tabular}
\end{table}
\subsection{Evaluation}
For our experiments, we employed 10-cross-validation on our dataset. We use partial evaluation by Seki et al. \cite{seki2003probabilistic} to get precision, recall, F1-measure for evaluation metrics. This evaluation is used because we treat keyphrases as sequences of words.

@@

For comparison, we implemented RAKE \cite{rake} and CRF \cite{cao2010automatically}, which use unsupervised and supervised approach. For CRF, we use the same features proposed above. We also conducted an experiment to proof the effectiveness of our CNN layer by comTM with CNNs layer(CNN-B-LSTM). Furthermore, we also compared our model with or without weighting layer (W-CNN-B-LSTM).

As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text. For CRF, based on our observation from the result provided by CRF, the method failed to predict long sequences as a keyphrase. Our CNNs layer also shows improvement in precision and F1 score when compared to standard B-LSTM. We suggest that CNNs layer can extract more features implicitly from neighboring words. Moreover, our weighting layer shows improvement compared to CNN-B-LSTM. Hence, the best result is obtained by W-CNN-LSTM.

We performed an analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example, "pusing pada (headache on)", "obat untuk (medicine for)". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our medical knowledge base or medical entities. Moreover, there are also special case that our model failed to handle. For example, "penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)", the keyphrase need to be captured as a whole because "sore throat" have a connection with the word "treatment". But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
\iffalse
We also ablate our model by removing our features one by one. As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature. Hence, we can say that all of our features are effective for this task.
 \begin{table}
	\caption{Average Change in Performance When Removing Each Feature}
	\label{tab:ablation}
	\begin{tabular}{cccc}
		\toprule
		Removed Features&Precision&Recall&F-Measure\\
		\midrule
            We & -4.08 & -18.34 & -12.84 \\
            Md & -8.35 & +0.24 & -3.84 \\
            Wl & -8.65 & +0.49 & -3.87 \\
            Wp & -9.77 & +2.44 & -3.5 \\
            Pt & -4.33 & -0.98 & -2.52 \\
            Wa & -5.57 & -1.96 & -3.62 \\
            Wi & -0.32 & -0.49 & -0.42 \\
            Me & -4.63 & +0.49 & -1.89 \\
            Ws & -7.62 & -2.2 & -4.73 \\
		\bottomrule
	\end{tabular}
\end{table}
\fi
\section{Conclusion}
We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain. Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text. Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm. We also proposed a new layer for weighting our features. Furthermore, Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing. Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.

>>>>

	\section{Introduction}
	The growth of internet access facilitates users to share and obtain contents about healthcare topic. These user-generated contents are actually potential sources for enriching medical-related knowledge, for which it can be very valuable for several tasks in IR and NLP.

	However, understanding those various health-related contents, especially from an online forum, is simply not a trivial task since they are written in free text format (i.e. unstructured format), and often prone to grammatical and typographical glitches. Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.

@@

	In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions from online forums, such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}. We present a new keyphrase extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated questions. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely in line with our goal since important keyphrases of a medical question can be used to formulate a query for the passage or question retrieval subsystem \cite{gong2009improving}. The following example shows the results of keyphrase extraction in a medical user-generated contents:
	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}. Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}. apakah ada hubungannya dengan \textbf{diet mayo}? terima kasih sblumnya dok.}
	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}. And when the symptom occur it's \textbf{very hurt when breathing}. is there any connection with \textbf{mayo diet}? thanks before)}

@@

	Sarkar and Kamal \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles. Stopwords was used by them  to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.

	As far as our knowledge, there are limited works regarding the task of keyphrase extraction from user-generated contents, especially in medical question. Cao et al. \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health forum. They use information, such as word location and length as features in their experiments.

@@

	\textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary. The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from Konsil Kedokteran Indonesia\footnote{www.
		kki.go.id/assets/data/arsip/SKDI\_Perkonsil,\_11\_maret\_13.pdf.}. The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug. Based on this feature, we classified words by their appearance in the medical dictionary. We represent this feature as one-hot-vector.

@@

	\textbf{Abbreviation and Acronym (Wa).} We also identified words by their appearance in abbreviation or acronym dictionary which was gathered manually. We observed that important word is rarely shortened by the users, such as "\texttt{"cancer", "flu", "bell's palsy"}. One-hot-vector is used to classify whether a word is an abbreviation/acronym or not.

@@

	\textbf{Word Stickiness (Ws).} As a keyphrase, a sequence must be in a valid order. There is some noise such as misused punctuation by users. For example, "\textit{Saya mengalami pusing pada jidat sakit perut dan pandangan kabur} (I am having a headache on forehead stomachache and blurred vision)", there is no comma between "jidat (forehead)", "sakit perut (stomachache)" and "dan (and)". Our model may mistaken the sequence "jidat sakit perut (forehead stomachache)" as a keyphrase. Based on that problem, we propose a feature that may capture how likely of a given word is occurred together with the word before and after. We leveraged a language model which use Pointwise Mutual Information (PMI) of a bigram probability to capture the problem. The language model was trained using documents from health-related online forum. Formula \ref{eq:pmi} is the formula for calculating the PMI value. In that formula, $p(x)$ is the occurrence probability of word $x$, $p(y)$ is the occurrence probability of word $y$, and $p(x, y)$ is the probability of word $x$ and $y$ co-occur together.
	\begin{equation}\label{eq:pmi}
	PMI(x,y)=log(\frac{P(x, y)}{P(x).P(y)})
	\end{equation}
	The feature function is formally described as $f_s(w) = [x, y]$ where $w$ is a word in a document, $x$ is the stickiness value between $w$ and the word before, and $y$ is the stickiness value between $w$ and the word before. For example, the word "\texttt{cancer}" in sentence "\texttt{How to prevent cancer doc?}", the feature value is $f_s(cancer) = [0.56, 0.1]$ where $f_s$ is feature stickiness feature function. It is worth to note that the word "\texttt{cancer}" is rarely co-occur with the word "\texttt{doc}". Therefore, the stickiness value between the word "\texttt{cancer}" and "\texttt{doc}" is relatively smaller than "\texttt{prevent}".

	\subsection{Proposed Model}
	We process the sequences word by word. All Features are extracted and concatenated into one vector from every word as the input representation of the model. The output of our model are labels which describe whether a word is either part of keyphrase or not.

@@

	To get a better inference, information from the past and future of sequences can be integrated. This approach is proven effective in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}. Therefore, we utilized bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.Then, we concatenate the output from both LSTM. We build up to two layers of B-LSTM.

@@

	We also experimented on customizing the way we input the features underneath our aforementioned model. Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to assign weights to every feature we have before the input fed into CNNs layer. 
	\begin{equation}\label{eq:concat}
	Z =  concatenate(F_{1}, F_{2}, ..F_{9})
	\end{equation}
	We argue that each feature has different contribution to the model. In order to do so, we create a new layer underneath our model to do the weighting scenario. Formally, let $Z$ is the input representation and $F_{i}$ are the extracted feature in vector form, $W_i \in {\rm I\!R^{a_i \times b}}$ where the length of $a$ is equal to $F_{i}$ and $b$ is the input representation vector. The following equation to weight all features can be seen in below:
	\begin{equation}
	Z =  tanh(W _{1}.F_{1} + W_{2}.F_{2} + .. + W_{n}.F_{9})
	\end{equation}

	\section{Evaluations and Results}
	\subsection{Data Collection}
	To develop training data, we collected question-answer pairs which previously crawled from Indonesian question-answering medical forum. Then, we removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs. Moreover, we also observed our data and defined the definition of keyphrase on user-generated medical domain so that the annotation process can be consistent. Finally, we manually annotated 416 questions. The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}.

@@

			\bottomrule
		\end{tabular}
	\end{table}
	\subsection{Evaluation}
	For our experiments, we employed 10-cross-validation on our dataset. We use partial evaluation which was proposed by Seki et al. \cite{seki2003probabilistic} to get precision, recall, F1-measure for evaluation metrics. This evaluation is used because we treat keyphrases as sequences labeling task.

@@

	For comparison, we implemented RAKE \cite{rake} and CRF \cite{cao2010automatically}. For CRF, we use the same features as proposed above. Moreover, We also conducted an experiment to proof the effectiveness of our CNNs layer by comparing B-LSTM with (CNN-B-LSTM) or without CNNs layer. We also compared our model with (W-CNN-B-LSTM) or without weighting layer.

	As we can see in Table \ref{tab:model_scenario}, RAKE performed the worst on Indonesian user-generated medical question since RAKE were specially devised for formal text. Of the other methods, CRF performed the worst. For CRF, based on our observation from the result provided by CRF, the method failed to predict long sequences as a keyphrase. Our CNNs layer also shows improvement in precision and F1 score when compared to standard B-LSTM. We suggest that CNNs layer can extract more features implicitly from neighboring words. Moreover, our weighting layer shows improvement compared to CNN-B-LSTM. Hence, the best result was obtained by W-CNN-LSTM. This is indicated that the feature weighting process worked well and could to some degree demonstrate the effectiveness of our model in keyphrase extraction for user-generated medical domain.

	We performed an analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example, "\texttt{pusing pada (headache on)}", "\texttt{obat untuk (medicine for)}". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our medical knowledge base or medical entities. Moreover, there are also special case that our model failed to handle. For example, "\texttt{penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)}", the keyphrase need to be captured as a whole because "\texttt{sore throat}" have a connection with the term "treatment for". But, our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
	\iffalse
	We also ablate our model by removing our features one by one. As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature. Hence, we can say that all of our features are effective for this task.
	\begin{table}
		\caption{Average Change in Performance When Removing Each Feature}
		\label{tab:ablation}
		\begin{tabular}{cccc}
			\toprule
			Removed Features&Precision&Recall&F-Measure\\
			\midrule
			We & -4.08 & -18.34 & -12.84 \\
			Md & -8.35 & +0.24 & -3.84 \\
			Wl & -8.65 & +0.49 & -3.87 \\
			Wp & -9.77 & +2.44 & -3.5 \\
			Pt & -4.33 & -0.98 & -2.52 \\
			Wa & -5.57 & -1.96 & -3.62 \\
			Wi & -0.32 & -0.49 & -0.42 \\
			Me & -4.63 & +0.49 & -1.89 \\
			Ws & -7.62 & -2.2 & -4.73 \\
			\bottomrule
		\end{tabular}
	\end{table}
	\fi
	\section{Conclusion}
	We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated contents in medical domain. Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text. Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm. We also proposed a new layer for weighting our features. Furthermore, Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing. Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.
